Synthesizing Symmetric Lenses

### 2019-04-18 papers/SymmetricLenses/rebuttal_icfp19.txt

BCP: I had not actually realized that we didn't prove that composition is
admissible!  This is a significant technical shortcoming, no?  Is the proof
hard?  Or is it maybe noit true?
AFM: The proof is quite hard, comparable to the near 100 page one done in
bijective lenses, not simpler like the QRE one. I don't personally consider
it a major shortcoming -- as I don't think it really is part of our core
contributions. I included a brief description of why it is hard.

    - There is no explanation of the selection of the benchmarks. What are their
      characteristics and why those exercise interesting aspects of the
      algorithm.

We describe the selection of the benchmark suite in section 6.1. 29 of the
benchmarks are taken from Augeas, a bidirectional tool for editing Linux
configuration files. These examples were quite large, and involved some very
complex transformations, though these benchmarks were typically bijective. These
demonstrated how our tool performed at large, complex transformations. The 8
benchmarks from Flash Fill provided a range of transformations, none of which
were not bijective. These demonstrated how our tool performed on tasks that lost
large amounts of data, and sometimes required extended transformations through
Expand. The remaining 11 benchmarks tested how our tool performed at the type of
transformations we are familiar with, from transformations that would be useful
in day-to-day software engineering or classic transformations from the
bidirectional programming literature.

KSF: In the above, we need to explain how we picked the examples in a way that 
didn't cherry pick ones that would work for us.  The above text doesn't do that.

@@

    - There is no attempt to explain what are the sources of worse performance
      for SS.

The primary impact on speed is the use of GreedySynth, instead of the bijective
RigidSynth. For GreedySynth, lenses are found between regular expressions that,
ultimately, do not show up in the final lens. RigidSynth does not incur this
performance penalty -- it only synthesizes lenses between regular expressions
for which there exists a bijective lens between them.

KSF: I'm not following the above argument, which makes me think the reviewers won't either. 
Can you revise to make the text more self-contained?

### 2019-04-18 papers/SymmetricLenses/rebuttal_icfp19.txt

* Regular expressions are widely understood, while few programmers know
  about programming with lenses.

* Each of the two regular expressions describes just one data format, while
  a lens has to deal with both at the same time.

* In the (common, in our experience) case where the natural way of writing
  the two formats puts Kleene stars in different places, manual lens
  programming requires mentally transforming both to a common "aligned"
  form, which can be quite challenging for programmers.  Our synthesis
  algorithm does this alignment automatically.

In our experiments, we manually programmed the regular expressions. While
writing these regular expressions, we did not massage them to be amenable to
synthesis. The synthesizer implements the star-semiring regular
expression equivalence axioms so that users do not have to worry about
the way they write expressions themselves.

@@

BCP: What would be an example of the last point?
AFM: Consider creating a lens of the following type: (a+b)* <=> (a*b)*a*.
Finding the identity lens between these two regular expressions would require
using sumstar, a regular expression equivalence we do not traverse.

    - What is the relationship between our information-theoretic ranking, and
      prior work like Unsupervised Learning by Program Synthesis

(afm: this can potentially go after the fold, as it was only mentioned in
passing, not as a critical question of the reviewer)
BCP: Maybe a short version here?
AFM: I couldn't find a natural way to split it into main component/subcomponent
so I just made it more terse

In a nutshell, Unsupervised Learning by Program Synthesis (ULPS)
learns a description of a single data set.  Ideally, such an
descriptions are compact and information theory is used as a measure
of the compactness of the description learned.  In this sense, ULPS
shares more similarities with Fisher et al's paper on "From Dirt To
Shovels" (which also seeks to learn a description of a single data
source) than it does with the current paper.

In contrast, in our current paper, we are attempting to learn a
translation from data set to another.  However, there are many different
candidate translations.  To select amongst the candidate translations,
we choose the translation that preserves as much information from
source to target (and vice versa) as possible.

In summary, both systems use information theory but the objectives of
the two systems are different and the properties measured by
information theory are also different.

(Please also see below for an extended response.)

@@

    - The authors do not consider lens compositions in their synthesis. Are
      there any justifications not to consider them? In existing results that
      synthesize bijective (quotient) lenses, one of the reasons not to consider
      lens composition in their synthesis is that ruling out them does not
      change the expressive power? Can you say a similar argument for this case?

We do not synthesize lens compositions for the same reasons as
previous work -- such compositions are quite difficult to generate
(doing so requires synthesizing an intermediate regular expression
from out of thin air).  We conjecture that adding composition lenses
would not increase the expressive power of the language but we have
not proven this fact.  The analogous proof for bijective lenses
required nearly 100 pages of work and we did not believe the result
was important enough to invest this amount of work.  We chose to focus
our energy on understanding the information theoretic ranking methods,
and the relationship between simple symmetric lenses and classical
symmetric lenses, which we view as the core contributions of this paper.

@@

    - There is no explanation of the selection of the benchmarks. What are their
      characteristics and why those exercise interesting aspects of the
      algorithm.

We describe the selection of the benchmark suite in section 6.1.

29 of the benchmarks are taken from Augeas, a bidirectional tool for editing Linux
configuration files.  We selected these 29 benchmarks by selecting
Augeas files one-by-one in alphabetical order (we did not cherry-pick
programs).  We stopped when we didn't feel that adding more benchmarks
would be informative.

These examples were quite large, and involved some very complex
transformations, though these benchmarks were typically
bijective. These benchmarks demonstrated how our tool performed on
large, complex transformations. The 8 benchmarks from Flash Fill
provided a range of transformations, none of which were not
bijective. Again, the FlashFill benchmarks were the first 8 benchmarks
in the paper.  These benchmarks demonstrated how our tool performed on
transformation tasks that
discard large amounts of data.  On occasion, these benchmarks require
the use of many regular expression equivalence axioms.  The remaining
11 benchmarks were chosen in an ad hoc manner --- we simply looked
around for useful day-to-day example data for which it would be useful to have lenses.

@@

    - There is no attempt to explain what are the sources of worse performance
      for SS.

Bijective synthesis is faster than symmetric synthesis because ...

### 2019-04-18 papers/SymmetricLenses/rebuttal_icfp19.txt

29 of the benchmarks are taken from Augeas, a bidirectional tool for editing Linux
configuration files.  We selected these 29 benchmarks by selecting
Augeas files one-by-one in alphabetical order (we did not cherry-pick
programs).  We stopped when we didn't feel that adding more benchmarks
would be informative.

These examples were quite large, and involved some very complex
transformations, though these benchmarks were typically
bijective. These benchmarks demonstrated how our tool performed on
large, complex transformations. The 8 benchmarks from Flash Fill
provided a range of transformations, none of which were not
bijective. Again, the FlashFill benchmarks were the first 8 benchmarks
in the paper.  These benchmarks demonstrated how our tool performed on
transformation tasks that discard large amounts of data.  On occasion,
these benchmarks require the use of many regular expression
equivalence axioms.  The remaining 11 benchmarks were chosen in an ad
hoc manner --- we simply looked around for useful day-to-day example
data for which it would be useful to have lenses.

    - There is no attempt to explain what are the sources of worse performance
      for SS.

Both the bijective synthesis and the symmetric synthesis use a pair of
collaborating synthesizers that involves (1) a search for a compatible
pair of regular expressions and (2) search for a lens given those
regular expressions.

Bijective synthesis is faster than symmetric synthesis because part
(2) is much faster.  More specifically, a bijection must translate
*all* data on the left into data on the right.  However, a symmetric
synthesis problem has a choice of *which* data on the left to translate
into data on the right.  This gives rise to a large set of possible
choices, and symmetric synthesis must consider all of them.

### 2019-04-19 papers/SymmetricLenses/rebuttal_icfp19.txt

BCP: What would be an example of the last point?
AFM: Consider creating a lens of the following type: (a+b)* <=> (a*b)*a*.
Finding the identity lens between these two regular expressions would require
using sumstar, a regular expression equivalence we do not traverse.

    - What is the relationship between our information-theoretic ranking, and
      prior work like Unsupervised Learning by Program Synthesis

(afm: this can potentially go after the fold, as it was only mentioned in
passing, not as a critical question of the reviewer)
BCP: Maybe a short version here?
AFM: I couldn't find a natural way to split it into main component/subcomponent
so I just made it more terse

In a nutshell, Unsupervised Learning by Program Synthesis (ULPS)
learns a description of a single data set.  Ideally, such 
descriptions are compact and information theory is used as a measure
of the compactness of the description learned.  In this sense, ULPS
shares more similarities with Fisher et al's paper on "From Dirt To
Shovels" (which also seeks to learn a description of a single data
source) than it does with the current paper.

@@

    - There is no explanation of the selection of the benchmarks. What are their
      characteristics and why those exercise interesting aspects of the
      algorithm.

We describe the selection of the benchmark suite in section 6.1.

29 of the benchmarks are taken from Augeas, a bidirectional tool for editing Linux
configuration files.  We selected these 29 benchmarks by selecting
Augeas files one-by-one in alphabetical order (we did not cherry-pick
programs).  We stopped when we didn't feel that adding more benchmarks
would be informative.

These examples were quite large, and involved some very complex
transformations, though these benchmarks were typically
bijective. These benchmarks demonstrated how our tool performed on
large, complex transformations. The 8 benchmarks from Flash Fill
provided a range of transformations, all of which were 
bijective. Again, the FlashFill benchmarks were the first 8 benchmarks
in the paper.  These benchmarks demonstrated how our tool performed on
transformation tasks that discard large amounts of data.  On occasion,
these benchmarks require the use of many regular expression
equivalence axioms.  The remaining 11 benchmarks were chosen in an ad
hoc manner --- we simply looked around for useful day-to-day example
data for which it would be useful to have lenses.

@@

    - p10:L466 for other reasons

The other reasons are to guarantee that any lens that is synthesized by our
synthesis algorithm is guaranteed to be well-typed.

    - p10:L489 relaxing this restrict is not problemantic

For all these combinators, we can follow the style of
unambiguity requirements on the types that was used in prior lens work. For
example, the original Boomerang paper explicitly includes such unambiguity
checks within the typing judgments; these unambiguity checks can be used in the
same way for the symmetric lens variants of these combinators.

@@

    - p12:L563-572 I would like to read more explanations on why
      \mathbb{H}^{\to} is defined as this.

In general, these derivations follow the information theory, so as to make
Theorem 3 true. Most strictly follow the rules of information theory.
The only ones that are more complex are merges. Calculating the expected
information to recover a string from a lens using merges does not involve a
simple inductive calculation, but requires reasoning about the probabilities of
individual strings in the unioned format, conditioned on the probabilities of
the source format.

### 2019-04-19 papers/SymmetricLenses/rebuttal_icfp19.txt

We do not synthesize lens compositions for the same reasons as
previous work -- such compositions are quite difficult to generate
(doing so requires synthesizing an intermediate regular expression
from out of thin air).  We conjecture that adding composition lenses
would not increase the expressive power of the language but we have
not proven this fact.  The analogous proof for bijective lenses
required nearly 100 pages of work and we did not believe the result
was important enough to invest this amount of work.  We chose to focus
our energy on understanding the information theoretic ranking methods,
and the relationship between simple symmetric lenses and classical
symmetric lenses, which we view as the core contributions of this paper.

    - There is no explanation of the selection of the benchmarks. What are their
      characteristics and why those exercise interesting aspects of the
      algorithm.

We describe the selection of the benchmark suite in section 6.1.

29 of the benchmarks are taken from Augeas, a bidirectional tool for
editing Linux configuration files.  We selected these benchmarks by
selecting Augeas files one-by-one in alphabetical order (we did
not cherry-pick programs).  We stopped when we didn't feel that
adding more benchmarks would be informative. These examples were
quite large, and involved some very complex transformations, though
these benchmarks were typically bijective. These benchmarks
demonstrated how our tool performed on large, complex transformations.

The 8 benchmarks from Flash Fill provided a range of transformations,
none of which were not bijective. Again, the FlashFill benchmarks were
the first 8 benchmarks in the paper.  These benchmarks demonstrated
how our tool performed on transformation tasks that discard large
amounts of data.  On occasion, these benchmarks require the use of
many regular expression equivalence axioms.

The remaining 11 benchmarks were chosen in an ad hoc manner --- we
simply looked around for day-to-day data formats for which it would
be useful to have lenses.

    - Why is symmetric synthesis slower than bijective synthesis.

Both the bijective synthesis and the symmetric synthesis engines use a
pair of collaborating synthesizers that involves (1) a search for a
compatible pair of regular expressions and (2) search for a lens given
those regular expressions.

@@

    - To add to the previous point: the evaluation could do a better job
      quantifying these limitations. For example, it would be good to see for
      each benchmark the size of annotations required, as well as how many
      "existing lenses" were used in compositional synthesis and where they came
      from (some standard library of lenses? or did the authors manually
      decompose each problem into subproblems? if so, then how many subproblems
      were there?)

There were a total of 12 uses of "require" in the benchmark suite. There were a
total of 4 uses of "skip" in the benchmark suite. In total 73 existing lenses
were used in compositional synthesis (about 1.5 per benchmark on average).
Typically, we manually decomposed these lenses, though some used the to_upper
function. We are happy to include a figure detailing the subtasks specified
during compositional synthesis in the final version of the paper (similar to the
one on p24 of Synthesizing Bijective Lenses).

    - Finally, the evaluation could also do a better job confirming that there's
      indeed a benefit to synthesizing a lens, rather than using a tool like
      FlashFill to synthesize the two functions independently. The related work
      section mentions that FlashFill cannot handle nested loops. However,
      FlashFill has evolved a lot since its original publication in 2011, so it
      would be interesting to see an empirical comparison.

We included an extended comparison to a current version of FlashFill in previous
work, and did not include such a comparison in this work for lack of space.

@@

While we do not need it in the algorithm, we include it to make formal claims
about bounding the cost. We describe why we need intervals for the formal claims
in 4.1.

=================================================================================
Reviewer B
=================================================================================

    - Theorem 1 is about the soundness of the equational theory shown in Fig. 4.
      Can you say the completeness?

The equational theory shown in Fig. 4. is incomplete, for it does not include
some of the non-star-semiring equivalences (for example: the regular expression
equivalence of (A | B)* = (A*B)*A* does not currently have an analogue in this
equational theory). Furthermore, it is currently unclear whether the natural
extensions to Conway's equational theory is sufficient for completeness, and
whether Kozen and Solomaa's deductive systems are easily amenable to SREs.

@@

    - p10:L489 relaxing this restrict is not problemantic

For all these combinators, we can merely straightforwardly follow the style of
unambiguity requirements on the types that was used in prior lens work. For
example, the original Boomerang paper explicitly includes such unambiguity
checks within the typing judgments, these unambiguity checks can be used in the
same way for the symmetric lens variants of these combinators.

    - p12:L563-572 I would like to read more explanations on why
      \mathbb{H}^{\to} is defined as this.

In general, these derivations are defined so as to make Theorem 3 true. Most of
these simply follow the decompositions provided by information theory, the
only ones that are more complex are merges. Calculating the expected information
to recover a string from a lens using merges does not involve a simple inductive
calculation, but requires reasoning about the probilities of individual strings
in the unioned format, conditioned on the probabilities of the source format.

### 2019-04-19 papers/SymmetricLenses/rebuttal_icfp19.txt

We do not synthesize lens compositions for the same reasons as
previous work -- such compositions are quite difficult to generate
(doing so requires synthesizing an intermediate regular expression
from out of thin air).  We conjecture that adding composition lenses
would not increase the expressive power of the language but we have
not proven this fact.  The analogous proof for bijective lenses
required nearly 100 pages of work and we did not believe the result
was important enough to invest this amount of work.  We chose to focus
our energy on understanding the information theoretic ranking methods,
and the relationship between simple symmetric lenses and classical
symmetric lenses, which we view as the core contributions of this paper.

    - There is no explanation of the selection of the benchmarks. What are their
      characteristics and why those exercise interesting aspects of the
      algorithm.

We describe the selection of the benchmark suite in section 6.1.

29 of the benchmarks are taken from Augeas, a bidirectional tool for
editing Linux configuration files.  We selected these benchmarks by
selecting Augeas files one-by-one in alphabetical order (we did
not cherry-pick programs).  We stopped when we didn't feel that
adding more benchmarks would be informative. These examples were
quite large, and involved some very complex transformations, though
these benchmarks were bijective. These benchmarks demonstrated 
how our tool performed on large, complex transformations.

The 8 benchmarks from Flash Fill provided a range of transformations,
none of which were bijective. Again, the FlashFill benchmarks were
the first 8 benchmarks in the paper.  These benchmarks demonstrated
how our tool performed on transformation tasks that discard large
amounts of data.  On occasion, these benchmarks require the use of
many regular expression equivalence axioms.

@@

    - To add to the previous point: the evaluation could do a better job
      quantifying these limitations. For example, it would be good to see for
      each benchmark the size of annotations required, as well as how many
      "existing lenses" were used in compositional synthesis and where they came
      from (some standard library of lenses? or did the authors manually
      decompose each problem into subproblems? if so, then how many subproblems
      were there?)

There were a total of 12 uses of "require" in the benchmark suite. There were a
total of 4 uses of "skip" in the benchmark suite. In total 73 existing lenses
were used in compositional synthesis (about 1.5 per benchmark on average).
Typically, we manually decomposed these lenses, though some used the to_upper
function. We are happy to include a figure detailing the subtasks specified
during compositional synthesis in the final version of the paper (similar to the
one on p24 of Synthesizing Bijective Lenses).

    - Finally, the evaluation could also do a better job confirming that there's
      indeed a benefit to synthesizing a lens, rather than using a tool like
      FlashFill to synthesize the two functions independently. The related work
      section mentions that FlashFill cannot handle nested loops. However,
      FlashFill has evolved a lot since its original publication in 2011, so it
      would be interesting to see an empirical comparison.

We included an extended comparison to a current version of FlashFill in previous
work, and did not include such a comparison in this work for lack of space. We
are happy to make comparison to FlashFill cited more explicitly.

@@

    - p10:L489 relaxing this restrict is not problemantic

For all these combinators, we can follow the style of
unambiguity requirements on the types that was used in prior lens work. For
example, the original Boomerang paper explicitly includes such unambiguity
checks within the typing judgments; these unambiguity checks can be used in the
same way for the symmetric lens variants of these combinators.

    - p12:L563-572 I would like to read more explanations on why
      \mathbb{H}^{\to} is defined as this.

In general, these derivations follow the information theory, so as to make
Theorem 3 true. Most strictly follow the rules of information theory.
The only ones that are more complex are merges. Calculating the expected
information to recover a string from a lens using merges does not involve a
simple inductive calculation, but requires reasoning about the probabilities of
individual strings in the unioned format, conditioned on the probabilities of
the source format. Because of this complexity, we chose to bound the information
content instead of calculate it exactly.

### 2019-04-19 papers/SymmetricLenses/rebuttal_icfp19.txt

Thank you for the thoughtful feedback. We first respond briefly to major
questions and concerns, then provide an (optional, "below the fold")
point-by-point response to individual concerns.

    - Why is writing two regexes easier for the user than writing a lens? Do
      input formats often come equipped with regexes already? Can the
      synthesizer use such pre-existing regexes out of the box, or do they
      have to be "massaged" by the user?

Writing regular expressions is significantly easier than programming lenses:

* Regular expressions are widely understood, whereas few programmers are
  fluent at building lenses.

* Each of the two regular expressions describes a single data format, while
  a lens has to deal with two formats at the same time.

@@

* In the (common, in our experience) case where the natural way of writing
  the two formats puts Kleene stars in different places, manual lens
  programming requires mentally transforming both to a common "aligned"
  form, which can be quite challenging for programmers.  Our synthesis
  algorithm does this alignment automatically.

In our experiments, we manually programmed the regular expressions. However,
when writing these regular expressions, we did not massage them to be
amenable to synthesis. The synthesizer implements the star-semiring regular
expression equivalence axioms, so that users do not have to worry about the
way they write expressions themselves.

@@

The remaining 11 benchmarks were chosen in an ad hoc manner --- we
simply looked around for day-to-day data formats for which it would
be useful to have lenses.

    - Why is symmetric synthesis slower than bijective synthesis.

Both the bijective synthesis and the symmetric synthesis engines use a
pair of collaborating synthesizers that involves (1) a search for a
compatible pair of regular expressions and (2) search for a lens given
those regular expressions.

Bijective synthesis is faster than symmetric synthesis because part
(2) is much faster.  More specifically, a bijection must translate
*all* data on the left into data on the right.  By contrast, a symmetric
synthesis problem has a choice of *which* data on the left to translate
into data on the right.  This gives rise to a large set of possible
choices, and symmetric synthesis must consider all of them.

@@

    - To add to the previous point: the evaluation could do a better job
      quantifying these limitations. For example, it would be good to see for
      each benchmark the size of annotations required, as well as how many
      "existing lenses" were used in compositional synthesis and where they came
      from (some standard library of lenses? or did the authors manually
      decompose each problem into subproblems? if so, then how many subproblems
      were there?)

There were a total of 12 uses of "require" in the benchmark suite. There were a
total of 4 uses of "skip" in the benchmark suite. In total 73 existing lenses
were used in compositional synthesis (about 1.5 per benchmark on average).
Typically, we manually decomposed these lenses, though some used the to_upper
function. We are happy to include a figure detailing the subtasks specified
during compositional synthesis in the final version of the paper (similar to the
one on p24 of Synthesizing Bijective Lenses).

    - Finally, the evaluation could also do a better job confirming that there's
      indeed a benefit to synthesizing a lens, rather than using a tool like
      FlashFill to synthesize the two functions independently. The related work
      section mentions that FlashFill cannot handle nested loops. However,
      FlashFill has evolved a lot since its original publication in 2011, so it
      would be interesting to see an empirical comparison.

We included an extended comparison to a current version of FlashFill in previous
work, and did not include such a comparison in this work for lack of space. We
are happy to make this comparison to FlashFill cited more explicitly.

### 2019-05-08 papers/SymmetricLenses/Conference/rebuttal_icfp19.txt

In summary, both systems use information theory but the objectives of
the two systems are different and the properties measured by
information theory are also different.

-----

    - The authors do not consider lens compositions in their synthesis. Are
      there any justifications not to consider them? In existing results
      that synthesize bijective (quotient) lenses, one of the reasons not to
      consider lens composition in their synthesis is that ruling out them
      does not change the expressive power? Can you say a similar argument
      for this case?

We do not synthesize lens compositions for the same reasons as in previous
work -- such compositions are quite difficult to generate (doing so requires
synthesizing an intermediate regular expression from out of thin air).

We conjecture that adding composition lenses would not increase the
expressive power of the language but we have not proven this.  (Honestly,
the analogous proof for bijective lenses required nearly 100 pages and we
did not believe the result was important enough to invest this amount of
work, since the whole algorithm relies on heuristics to terminate in a
reasonable amount of time anyway.)  We chose to focus our energy on
understanding the information-theoretic ranking methods, and the
relationship between simple symmetric lenses and classical symmetric lenses,
which we view as the core contributions of this paper.

-----

@@

    - There is no explanation of the selection of the benchmarks. What are
      their characteristics and why those exercise interesting aspects of
      the algorithm.

We describe the selection of the benchmark suite in section 6.1.

29 of the benchmarks are taken from Augeas, a bidirectional tool for editing
Linux configuration files.  We chose these benchmarks by selecting Augeas
files one-by-one in alphabetical order (we did not cherry-pick programs).
We stopped when we didn't feel that adding more benchmarks would be
informative. These examples were fairly large and involved some quite
complex transformations, though only bijective ones. The purpose of these
benchmarks was to demonstrate how our tool performed on large, complex
transformations.

The 8 benchmarks from Flash Fill (the first 8 in the paper) illustrate a
range of sample transformations, none of them bijective.  These benchmarks
demonstrate how our tool performs on transformation tasks that _discard_
large amounts of data.  Some of them require the use of many regular
expression equivalence axioms.

The remaining 11 benchmarks were chosen in an ad hoc manner: we simply
looked around for day-to-day data formats for which it would be useful to
have lenses.

-----

@@

    - Why is symmetric synthesis slower than bijective synthesis.

Both the bijective synthesis and the symmetric synthesis engines use a pair
of collaborating synthesizers that involves (1) a search for a compatible
pair of regular expressions and (2) search for a lens given those regular
expressions.

Bijective synthesis is faster than symmetric synthesis because part (2) is
much faster.  Specifically, a bijection must translate *all* data on the
left into data on the right, and this fact constrains the search.  By
contrast, a symmetric synthesis problem has a choice of *which* data on the
left to translate into data on the right.  This gives rise to a large set of
possible choices, and symmetric synthesis must consider all of them.

(Detailed responses to the reviews follow.  The rest of the file is optional.)
=================================================================================
Reviewer A
=================================================================================

@@

Below is an explicit example of of the difficulty of writing lenses vs writing
regular expressions.

        let last_head = NAME . "," . (WSP . NAME)*
        let last_tail = (NAME . WSP)* NAME

        let name_conversion : last_head <=> last_tail =
            lens_swap
                (NAME . del ",")
                (lens_swap WSP NAME)*

While the name_conversion lens has about as many AST nodes than the two
regular expressions, we find it much trickier to write.

Arguably, these regular expressions are useful to write anyway -- after all,
good engineering practice often recommends annotating programs with their
types!  While Boomerang does not require these annotations - being able to
infer the types from the terms - the types of the term do serve as
documentation for future programmers to understand what formats the lens
maps between, and this may be especially useful if the lens itself is
synthesized.  Furthermore, type annotationss provide resilience in the face
of future changes, as the types ensure that the lens maps exactly between
strings of the provided formats.

-----

@@

    - Moreover, on top of the regexes, the user needs to provide examples and
      relevance annotations, and the only way to do so seems to be through an
      iterative process (by inspecting the synthesized lens and adding more
      examples / annotations when needed). Such iterative approach would be
      challenging for a user who is not sufficiently familiar with lenses to
      write one themselves.

We described the iterative process assuming a lazy user who didn't want to
provide more specifications than were necessary. However, such an iterative
process is not required, and if the user is confident that certain information
is "required" or may safely "skipped," they can safely add this information; 
it will not slow down synthesis. Similarly, if the user already has a benchmark
suite, they may safely include all of it right at the beginning.

-----

@@

    - To add to the previous point: the evaluation could do a better job
      quantifying these limitations. For example, it would be good to see for
      each benchmark the size of annotations required, as well as how many
      "existing lenses" were used in compositional synthesis and where they came
      from (some standard library of lenses? or did the authors manually
      decompose each problem into subproblems? if so, then how many subproblems
      were there?)

There were a total of 12 uses of "require" in the benchmark suite. There
were a total of 4 uses of "skip" in the benchmark suite. In total 73
existing lenses were used in compositional synthesis (about 1.5 per
benchmark on average).  Typically, we manually decomposed these lenses,
though some used the to_upper function. (We like the idea of including a
figure detailing the subtasks specified during compositional synthesis in
the final version of the paper, similar to the one on p24 of Synthesizing
Bijective Lenses.)

-----

@@

    - Finally, the evaluation could also do a better job confirming that there's
      indeed a benefit to synthesizing a lens, rather than using a tool like
      FlashFill to synthesize the two functions independently. The related work
      section mentions that FlashFill cannot handle nested loops. However,
      FlashFill has evolved a lot since its original publication in 2011, so it
      would be interesting to see an empirical comparison.

We included an extended comparison to a current version of FlashFill in
previous work, but did not include such a comparison in this work for lack
of space. We are happy to cite this comparison to FlashFill more explicitly.

-----

@@

While we do not need it in the algorithm, we include it to make formal
claims about bounding the cost. We describe why we need intervals for the
formal claims in 4.1.

=================================================================================
Reviewer B
=================================================================================

    - Theorem 1 is about the soundness of the equational theory shown in Fig. 4.
      Can you say the completeness?

The equational theory shown in Fig. 4. is incomplete: it does not include
some of the non-star-semiring equivalences (for example: the regular
expression equivalence of (A | B)* = (A*B)*A* does not currently have an
analogue in this equational theory). Furthermore, it is currently unclear to
us whether the natural extension to Conway's equational theory is sufficient
for completeness, or whether Kozen and Solomaa's deductive systems are
easily amenable to SREs.

-----

@@

The other reasons are to guarantee that any lens that is synthesized by our
synthesis algorithm is guaranteed to be well-typed.

-----

    - p10:L489 relaxing this restrict is not problemantic

For all these combinators, we can follow the style of "unambiguity
requirements" on the types that was used in prior lens work. For example,
the original Boomerang paper explicitly includes such unambiguity checks
within its typing judgments; these unambiguity checks can be used in the
same way for the symmetric lens variants of these combinators.

-----

@@

This is done by looking at the example parses. For example, given two regular
expressions "a" | "b" and "c", and the example data putl "c" "b" = "a", we can
determine that there cannot be a lens between "c" and "b".

=================================================================================
Reviewer C
=================================================================================

    - 5 runs per benchmark are not sufficient to draw statistically significant
      conclusions. There is no report of errors or confidence intervals for the
      mean time calculations.

We only ran five times because there was so little variance between the times, as
our procedure is deterministic. Rerunning, we found our average standard
deviation while running the full symmetric algorithm was .0162. We are happy
to both include standard deviations and rerun additional times.

-----

@@

In general, SS always performs better than SSNC and SS always performs worse
than BS. We ran for 30s under the assumption that users would be unwilling to
wait for responses much longer than that. We are happy to rerun with a longer
timeout.

-----

    - Similar to the above, the graph in figure 8 and the accompanying
      discussion are not sufficient to understand what features of the algorithm
      help or do not help with what kind of inputs.

"Require"s help with continuing searching when the desired lenses require a
large number of Expand applications. "Skip"s help when the desired lenses
involve projecting large amounts of information. Using the DC metric only
works for lenses where the desired lens appears quite early. FL is the same
as DC, but is even more dependent on the desired lens appearing early (it
*must* appear in the first cluster containing a satisfying program).
